Sequence data processing

### 2022-05-25 R/07-process-community.Rmd
remove phyloseq and replace with tibbles
revise processing script and shrink otu table

flux_sd <- 
  fluxes %>% 
  mutate(sample = paste0('G', passage, toupper(treat), rep)) %>% 
  select(sample, flux_date:selected) %>% 
  mutate(passage = as.character(passage))

flux_sd <-
  flux_sd %>% 
  select(sample, ch4, selected)

full_data <-
  aes_data %>% 
  left_join(flux_sd, by = "sample")

write_tsv(full_data, 'Output/communty_data.tsv')

@@

```{r old-stuff, eval = FALSE}

samples_filtered <- 
filter(samples, sample_id %in% flux_sd$sample)

fluxes_filtered <- 
  filter(flux_sd, sample_id %in% samples$sample_id) %>% 
  as.data.frame()

>>>>

flux_sd <- 
  fluxes %>% 
  mutate(sample = paste0('G', passage, toupper(treat), rep)) %>% 
  select(sample, flux_date:selected) %>% 
  mutate(passage = as.character(passage)) %>% 
  select(sample, ch4, selected)

full_data <-
  aes_data %>% 
  filter(!treat %in% c("NC0",  "PM0",  "SC0",  "PCRP", "PCRN")) %>% 
  select(-c(row, col, qubit_ngml)) %>% 
  left_join(flux_sd, by = "sample")

# Remove zero-abundance ASVs
full_data <-
  full_data %>% 
  group_by(asv) %>% 
  mutate(total = sum(count)) %>% 
  filter(total != 0) %>% 
  ungroup() %>% 
  select(-total) %>% 
  filter(count > 0)

write_tsv(full_data, 'Output/community_data.tsv')

@@
